Reproducible Research Practices and Barriers to Reproducible Research in Geography: Insights from a Survey

### 2022-11-10 docs/manuscript/manuscript.tex

The available body of direct and indirect reproducibility assessments currently provides

insufficient evidence to conclusively evaluate the reproducibility of scientific research generally, or disciplinary research specifically \citep{NASEM2019}.
This knowledge gap exists in part because while available evidence consistently suggests that inadequate record keeping, opaque reporting, and unavailable research components are drivers of research irreproducibility, how common these practices are remains unclear. 
We have been unable to estimate the prevalence and impact of these practices because indirect assessments have used non-probability based sampling methods to draw data from non-representative, self-selected populations (e.g., professional association memberships).

Prior surveys have also commonly failed to systematically report the methodological details (e.g., response rate) needed to assess and address potential bias.

Surveys of researchers working across the sciences suggest that the majority of scientists have either not tried, or tried and failed to reproduce another scientist's work \citep{baker20161, boulbes2018survey}. 
Perceptions on the cause of irreproducibility range from natural variation to fraud \citep{ranstam2000fraud, anderson2007normative, baker20161}, with an estimated 33 percent of researchers admitting to some form of questionable research practices \citep{fanelli2009many}.  
Researchers also appear to support a broad range of solutions to the challenge of irreproducibility including improved training in research design and statistics and better research mentoring and supervision \citep{baker20161}.

\subsection*{Assessing the Reproducibility of Geographic Research}
Direct and indirect assessments of research reproducibility

>>>>

Despite their growing number, the available body of direct and indirect reproducibility assessments currently provides insufficient evidence to conclusively evaluate the reproducibility of research generally, or disciplinary research specifically \citep{NASEM2019}.
This knowledge gap exists because neither direct nor indirect reproducibility assessments have been designed so the results of the sample of studies evaluated can be extended to the population of research as a whole. 
Reproduction attempts remain relatively rare, and those that do exist \citep[see][]{chang2015economics, moraila2014measuring} have selectively targeted publications in high-impact journals and conference papers series in a limited number of disciplines that are not representative of many forms of research.    
Indirect reproducibility assessments that catalog the availability of research components similarly focus on conveniently accessible archives, such as conference paper series \citep{gundersen2018state, ostermann2017}, or target specific journals and disciplinary repositories \citep{stodden2018empirical, stodden2018enabling, byrne_2017}.
These assessments have also tended to focus on evaluating the computational components of research such as data and code availability, as this information is easier to identify and assess at scale when compared to components like field procedures or qualitative analysis that may be included only in text. 
Surveys of researcher practices and attitudes on reproducibility face similar challenges to their generalizability. 
Rather than carefully defining researcher populations of interest, prior surveys have drawn data non-randomly from self-selecting populations that are convenient to survey (e.g., members of professional association, conference attendees), but are not necessarily representative of researchers active in a particular field. 
These surveys have also commonly failed to systematically report the methodological details (e.g., response rate) needed to assess and address potential bias in survey response.

While it may not be possible to determine the extent of irreproducibility across or within disciplines, it is possible to draw lessons about potential sources of irreproducibility from available studies.
The evidence available from direct and indirect reproducibility assessments suggests inadequate record keeping, opaque reporting, unavailable research components, and a lack of incentives are important factors contributing to the irreproducibility of research \citep{NASEM2019}. 
Prominent attempts to reproduce research in economics \citep{chang2015economics}, computer science \citep{moraila2014measuring}, and psychology \citep{open2015estimating} have all been able to reproduce only a small portion of studies because original authors did not share data or adequate information about their procedures. 
Systematic reviews of publications in prominent outlets \citep{byrne_2017,stodden2018empirical} suggest these issues are likely widespread, as the majority of articles reviewed did not share data adequate for reproducibility.

Surveys of researchers about reproducibility issues and related research practices paint a similar picture. 
Recent surveys suggest that the majority of scientists have either not tried, or tried and failed to reproduce another scientist's work \citep{baker20161, boulbes2018survey}. 
Moreover, a sizable portion of the researchers responding to these surveys admit to engaging in questionable research practices linked to the publication of false positive results and low reproducibility rates \citep{fanelli2009many, fraser2018questionable}.
For example, in a survey of 807 ecologists and evolutionary biologists, 64 percent admitted to failing to report non-significant results and 51 percent admitted to presenting unexpected findings as if they been hypothesized from the start of the research \citep{fraser2018questionable}.  
These findings also match researcher perceptions, which link irreproducibility to causes ranging from natural variation to outright fraud \citep{ranstam2000fraud, anderson2007normative, baker20161}.

\subsection*{Assessing the Reproducibility of Geographic Research}
Reproducibility has only recently moved forward on Geography's disciplinary research agenda.

Direct and indirect assessments of research reproducibility
